---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

# Lesson with Code

<!-- Google Slide ID -->
<!-- 1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg -->

<!-- Include a slide PNG with Page_ID from this Slide Deck: -->
<!-- ![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=PAGE_ID) -->
<!-- or use  `didactr::gs_slide_df("1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg")$png_markdown` -->


### Sections

<!-- Notes from Slide p-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=p)

<!-- Notes from Slide g154a28a8c9_0_254-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g154a28a8c9_0_254)

<!-- Notes from Slide g154a28a8c9_0_258-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g154a28a8c9_0_258)

<!-- Notes from Slide g154aa4fae2_0_50-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g154aa4fae2_0_50)

<!-- Notes from Slide g154aa4fae2_0_58-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g154aa4fae2_0_58)

<!-- Notes from Slide g154aa4fae2_0_65-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g154aa4fae2_0_65)

<!-- Notes from Slide g154aa4fae2_0_73-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g154aa4fae2_0_73)

<!-- Notes from Slide g154a28a8c9_0_266-->


```{r g154a28a8c9_0_266}
#rstats
superheroes <-
  c("    name, alignment, gender,         publisher",
    " Magneto,       bad,   male,            Marvel",
    "   Storm,      good, female,            Marvel",
    "Mystique,       bad, female,            Marvel",
    "  Batman,      good,   male,                DC",
    "   Joker,       bad,   male,                DC",
    "Catwoman,       bad, female,                DC",
    " Hellboy,      good,   male, Dark Horse Comics")

superheroes <- read.csv(text = superheroes, strip.white = TRUE)
```

{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g154a28a8c9_0_266)

<!-- Notes from Slide g154a28a8c9_0_272-->


```{r g154a28a8c9_0_272}
publishers <- 
  c("publisher, yr_founded",
    "       DC,       1934",
    "   Marvel,       1939",
    "    Image,       1992")
publishers <- read.csv(text = publishers, 
strip.white = TRUE)
```

{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g154a28a8c9_0_272)

<!-- Notes from Slide g154aa4fae2_0_9-->


```{r g154aa4fae2_0_9}
ijsp = inner_join(superheroes, publishers)
```

{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g154aa4fae2_0_9)

<!-- Notes from Slide g154aa4fae2_0_18-->


```{r g154aa4fae2_0_18}
ljsp = left_join(superheroes, publishers)

```

{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g154aa4fae2_0_18)

<!-- Notes from Slide g154aa4fae2_0_36-->


```{r g154aa4fae2_0_36}
fjsp <- full_join(superheroes, publishers)
```

{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g154aa4fae2_0_36)

<!-- Notes from Slide g154aa4fae2_0_85-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g154aa4fae2_0_85)

<!-- Notes from Slide g154a28a8c9_0_283-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g154a28a8c9_0_283)

<!-- Notes from Slide g15cbe86ce4_0_31-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_31)

<!-- Notes from Slide g15cbe86ce4_0_37-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_37)

<!-- Notes from Slide g15cbe86ce4_0_46-->


```{r g15cbe86ce4_0_46}
install.packages('dplyr')
install.packages('dbplyr')
install.packages('babynames')
install.packages('pryr')
library(dplyr)
library(dbplyr)
library(babynames)
library(pryr)
```

{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_46)

<!-- Notes from Slide g15cbe86ce4_0_63-->


```{r g15cbe86ce4_0_63}
?babynames
View(babynames)
str(babynames)
object_size(babynames)
```

{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_63)

<!-- Notes from Slide g15cbe86ce4_0_51-->


```{r g15cbe86ce4_0_51}
my_db <- src_sqlite("my_db.sqlite3", 
create = T)
babys_sqlite <- copy_to(my_db, 
babynames, temporary = FALSE)
src_tbls(my_db)
tbl(my_db,"babynames")
```

{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_51)

<!-- Notes from Slide g15cbe86ce4_0_70-->


```{r g15cbe86ce4_0_70}
newtbl = my_db %>% 
tbl("babynames")%>% 
filter(name=="Hilary") %>% 
select(year,n,name)
newtbl
```

{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_70)

<!-- Notes from Slide g15cbe86ce4_0_76-->


```{r g15cbe86ce4_0_76}
newtbl = my_db %>% 
tbl("babynames")%>% 
filter(name=="Hilary") %>% 
select(year,n,name)
newtbl
```

{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_76)

<!-- Notes from Slide g15cbe86ce4_0_83-->


```{r g15cbe86ce4_0_83}
newtbl = my_db %>% 
tbl("babynames")%>% 
filter(name=="Hilary") %>% 
select(year,n,name)
output = newtbl %>% collect()
```

{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_83)

<!-- Notes from Slide g15cbe86ce4_0_90-->


```{r g15cbe86ce4_0_90}
popular = babynames %>%
  group_by(name) %>%
  summarise(N = sum(n)) %>%
arrange(desc(N)) %>% top_n(100)
```

{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_90)

<!-- Notes from Slide g15cbe86ce4_0_100-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_100)

<!-- Notes from Slide g15cbe86ce4_0_112-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_112)

<!-- Notes from Slide g15cbe86ce4_0_118-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_118)

<!-- Notes from Slide g15cbe86ce4_0_128-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_128)

<!-- Notes from Slide g15cbe86ce4_0_144-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_144)

<!-- Notes from Slide g15cbe86ce4_0_157-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_157)

<!-- Notes from Slide g15cbe86ce4_0_168-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_168)

<!-- Notes from Slide g154aa4fae2_0_91-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g154aa4fae2_0_91)

<!-- Notes from Slide g23d7fee4da_0_109-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g23d7fee4da_0_109)

<!-- Notes from Slide g15cbe86ce4_0_0-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_0)

<!-- Notes from Slide g15cbe86ce4_0_6-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_6)

<!-- Notes from Slide g15cbe86ce4_0_20-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_20)

<!-- Notes from Slide g15cbe86ce4_0_26-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_26)

<!-- Notes from Slide g15cbe86ce4_0_180-->


```{r g15cbe86ce4_0_180}
write_csv(babynames,
file="babynames.csv")
system.time(read.csv('babynames.csv'))
system.time(read_csv('babynames.csv'))
system.time(fread('babynames.csv'))
```

{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_180)

<!-- Notes from Slide g15cbe86ce4_0_186-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_186)

<!-- Notes from Slide g15cbe86ce4_0_194-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_194)

<!-- Notes from Slide g15cbe86ce4_0_199-->


```{r g15cbe86ce4_0_199}
baby_dt[sex=="F",.(name,mean(prop))]
baby_dt[sex=="F",
.(name,mean(prop)),name]
baby_dt[sex=="F",
.(name,aveprop=mean(prop)),name]
baby_dt[,aveprop:=mean(prop),name]


#rstats
```

{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_199)

<!-- Notes from Slide g15cbe86ce4_0_205-->


{format: png}
![](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/export/png?id=1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg&pageid=g15cbe86ce4_0_205)


### Summary

### Additional Resources

### Slides and Video

<!-- ![Lesson with Code](YouTube Link) -->

* [Slides](https://docs.google.com/presentation/d/1X76ckIsLaNjw1AQGuiG5VK5nRgIah0JSQ8xGpfs9jtg/edit?usp=sharing)


{quiz, id: quiz_01_lesson_with_code}

### Lesson with Code quiz

{choose-answers: 4}
? 

C) The answer to this one
o) Not the answer

C) 
m)

{/quiz}


